### 2013-12-17 poster_new/conference_poster_4.tex
height adjustment (almost)

\headerbox{EXPERIMENTAL SETUP}{name=exp,column=1,row=0}{
\begin{itemize}
%\item We simulated a dummy control application on both hierarchical and flat controller architectures, with same network topology and flow arrival distribution.
\item Flow data (6000 MapReduce jobs) was generated by sampling historical Hadoop traces on a 600 machine cluster at Facebook (1 million jobs). A dummy MapReduce application choses directory, map and reduce nodes randomly for each job.
\item Topology: 600 hosts connected through a network of 200 switches and 10 Gbps links. The cluster is divided into 10 equally-sized control domains.
\item TE-cum-routing control application: When a new flow arrives, it finds the path with minimum maximum utilization. If multiple such paths exist (which is frequently the case, due to a large network), shortest path (in term of number of hops) is chosen.
\end{itemize}
}

@@

\begin{multicols}{2}
\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.2]{path.png}
\captionof{figure}{Path length}
\label{fig:path}
\end{center}
\end{minipage}

\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.2]{util.png}
\captionof{figure}{Maximum link utilization}
\label{fig:util}
\end{center}
\end{minipage}
\end{multicols}

@@

\headerbox{RESULTS}{name=results,column=1,below=metrics}{
    \begin{itemize}
        \item Reduces communication overhead by TODO (Figure \ref{fig:msg})
        \item Increases shortest path length by 17.4\% (Figure \ref{fig:path})
        \item Increases minimum maximum link utilization by 12.8\% (Figure \ref{fig:util}).
    \end{itemize}
Hierarchical architecture reduces communication overhead by an order of magnitude while compromising modestly on optimality
}

>>>>

\headerbox{EXPERIMENTAL SETUP}{name=exp,column=1,row=0}{
\begin{itemize}
%\item We simulated a dummy control application on both hierarchical and flat controller architectures, with same network topology and flow arrival distribution.
\item Flow data (6000 MapReduce jobs) was generated by sampling historical Hadoop traces on a 600 machine cluster at Facebook (1 million jobs).
\item A dummy MapReduce application choses directory, map and reduce nodes randomly for each job.
\item Topology: 600 hosts connected through a network of 200 switches and 10 Gbps links. The cluster is divided into 10 equally-sized control domains.
\item TE-cum-routing control application: When a new flow arrives, it finds the path with minimum maximum utilization. If multiple such paths exist (which is frequently the case, due to a large network), shortest path (in term of number of hops) is chosen.
\end{itemize}
}

@@

\begin{multicols}{2}
\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.22]{path.png}
\captionof{figure}{Path length}
\label{fig:path}
\end{center}
\end{minipage}

\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.22]{util.png}
\captionof{figure}{Maximum link utilization}
\label{fig:util}
\end{center}
\end{minipage}
\end{multicols}

@@

\headerbox{RESULTS}{name=results,column=1,below=metrics}{
    \begin{itemize}
        \item Reduces communication overhead by 90.5\% (Figure \ref{fig:msg}).
        \item Increases shortest path length by 17.4\% (Figure \ref{fig:path}).
        \item Increases minimum maximum link utilization by 12.8\% (Figure \ref{fig:util}).
    \end{itemize}
Hierarchical architecture reduces communication overhead by an order of magnitude while compromising modestly on optimality.
}
